\stepcounter{subsection}

\beginsong{The bonny ship the diamond}[%
    by={\textit{Traditional}},
    index={thebonnyshipthediamond}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad The bonny ship the diamond --- \textit{Traditional}}

    \label{thebonnyshipthediamond}

    \begin{center}
        \gtab{Am}{X02210:002310}
        \gtab{Em}{022000:023000}
        \gtab{Em7}{020000:020000}
    \end{center}

    \beginverse
        The \[Am]Diamond is a \[Em]ship me lads, for the \[Am]David Straits she's \[Em]bound
        \[Am]And the quay it is all \[Em]garnished with \[Am]bonny \[Em7]lassies \[Am]round.
        Captain \[Am]Thompson gives the \[Em]order to \[Am]sail the ocean \[Em]wide
        Where the \[Am]sun it never \[Em]sets me lads, nor \[Am]darkness \[Em7]dims the \[Am]
    \endverse

    \beginchorus
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus

    \beginverse
        A^long the quay at ^Peterhead the ^lassies stand a^round
        With their ^shawls pulled all a^bout them and the ^salt ^tears running ^down.
        ^Don't you weep me ^bonny lassie, though ^you'll be left be^hind
        For the ^rose that grows on ^Greenland's ice be^fore I ^changed my ^mind.
    \endverse

    \beginchorus
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus

    \beginverse
        Here's ^health to the Reso^lution, like^wise the Eliza ^Swan.
        Here's ^health to the Battler of ^Montrose and the ^Diamond ^ship of ^fame.
        We ^wear the trousers ^of the white and the ^jackets of the ^blue
        When ^we return to ^Peterhead we'll ^hae sweet^hearts en^ou'.
    \endverse

    \beginchorus
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus

    \beginverse
        ^It'll be bright both ^day and night when the ^Greenland lads come ^hame
        With a ^ship that's full of ^oil me lads and ^money ^to our ^name.
        We'll ^make the cradles ^for to rock and the ^blankets for to ^tear
        And ^ev'ry lass in ^Peterhead sing ^Hush a ^bye me ^dear
    \endverse

    \beginchorus
        \textnote{2x}
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus
\endsong
