% vim: ft=tex:

\stepcounter{subsection}

\beginsong{Lives in the Balance}[%
    by={Jackson Browne},
    index={livesinthebalance}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{Lives in the Balance} --- Jackson Browne}

    \label{livesinthebalance}

    \textbf{Note: this song is not yet finished!}

    \beginverse
        I've been waiting for something to happen
        For a week or a month or a year
        With the blood in the ink of the headlines
        And the sound of the crowd in my ear.
        You might ask what it takes to remeber
        When you know that you've seen it before
        Where a gobvernment lies to a people
        And a country is drifting to war
    \endverse

    \beginchorus
        There's a shadow on the faces
        Of the men who send the guns
        To the wars that are fought in places
        Where their business interests runs
    \endchorus

    \beginverse
        On the radio talk shows and the TV
        You hear one thing again and again
        How the USA stands for freedom
        And we come to the aid of a friend
        But who are the ones that we call our friends?
        These governments killing their own?
        Or the people who finally can't take anymore
    \endverse

    \beginchorus
        And they pick up a gun or a brick or a stone
        There are lives in the balance \echo{There are!}
        There are people under fire \echo{There are!}
        There are children at the cannons \echo{There are!}
        And there is blood on the wire
    \endchorus

    \beginchorus
        There's a shadow on the faces
        Of the men who fan the flames
        Of the wars that are fought in places
        Where we can't even say their names
    \endchorus

    \beginverse
        They sell us the president the same way
        They sell us our clothes and our cars
        They sell uis everything from youth to religion
        The same time they sell us our wars
        I wanna know who the men in the shadows are
        I wanna hear somebody asking them why
        They can be counted on to tell us who our enemies are
    \endverse

    \beginchorus
        But they're never the ones to fight or to die
        There are lives in the balance \echo{There are!}
        There are people under fire \echo{There are!}
        There are children at the cannons \echo{There are!}
        And there is blood on the wire
    \endchorus

    \beginchorus
        There are lives in the balance
        There are people under fire
        There are children at the cannons

        THERE ARE ... !
    \endchorus
\endsong
