% vim: ft=tex

\stepcounter{subsection}

\beginsong{Cheap Flights}[%
    by={Fascinating Aida},
    cr={},
    li={},
    index={cheap_flights}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{Cheap Flights} --- Fascinating Aida}

    \label{cheap_flights}

    %\begin{center}
        %\gtab{C}{332010:342010}     % \gtab{<CHORDNAME>}{<FRETS>}{<FINGERING>}
        %\gtab{G}{320033:210034}
        %\gtab{F}{133411:134211}
    %\end{center}

    \beginverse\memorize[verse]
        We received an invitation in the post one Monday morn'
        To attend our cousin's wedding in the town where we were born.
        The do was back in Kerry; so wishing to be frugal.
        We trawled the 'net to find some decent travel deals on Google.
    \endverse

    \beginchorus\memorize[chorus]
        Cheap flights, cheap flights, cheap as they can be,
        Bedad we found an airline selling flights for 50p.
    \endchorus

    \beginverse\replay[verse]
        Well we clicked on to the website and were mightily surprised,
        To find the actual cost wasn't quite as advertised.
        We'd forgotten airport taxes, had also to be billed,
        But a bargain is a bargain and begorrah we were thrilled.
    \endverse

    \beginchorus\replay[chorus]
        Cheap flights, cheap flights, Stanstead to Tralee,
        It isn't every airline offers flights for 50p.
    \endchorus

    \beginverse\replay[verse]
        After studying the website we decided it was best,
        To pay priority boarding so that we'd sit three abreast.
        And of course we'd all have luggage, so that's an extra cost,
        And then we paid insurance in case our cases might get lost.
    \endverse

    \beginchorus\replay[chorus]
        Our cheap flights, cheap flights, it's obvious to see,
        There must be extra charges when the flights are 50p.
    \endchorus

    \beginverse\replay[verse]
        At last the flight was booked, with all of the additions,
        We'd read the reams of smallprint, of terms and conditions;
        And then picked up the charge for using VISA which was drastic,
        'Cause how the feck are you supposed to pay if not with fecking plastic?
    \endverse

    \beginchorus\replay[chorus]
        Cheap flights, cheap flights, we paid the fecking fee,
        Because by now we were committed to the flights for 50p.
    \endchorus

    \beginverse\replay[verse]
        Now I don't know if you've tried locating Stanstead on a map,
        But checking in at 5am is a fecking load of crap,
        It's packed if you try to catch a train or underground,
        So a taxi to the arse in the world was more than 100 pounds,
    \endverse

    \beginchorus\replay[chorus]
        Cheap flights, cheap flights, we should have gone by sea,
        There's no such a fecking thing as a fecking flight for 50p.
    \endchorus

    \beginverse\replay[verse]
        Then at last we reached the airport where we had to pay a fine,
        The fecking feckers charged us 'cause we hadn't checked in online,
        And finally aboard the flight there's an extra class of tax,
        'Cause the fecking fecking feckers fecking charge to use the jacks,
    \endverse

    \beginchorus\replay[chorus]
        Cheap flights, cheap flights, I think you must agree,
        That only fecking gobshites think there's flights for 50p.
    \endchorus

    \beginverse\replay[verse]
        Well finally we landed and tried to shuffle up the aisle
        But the steward sent us down to the back with never a hint of s(ch)mile
        And as we heard his announcement our hearts gave a terrible thump.
        If you haven't prepaid to use the steps you'll have to feckin' jump!
    \endverse

    \beginchorus\replay[chorus]
        Cheap flights, cheap flights, you're harking on to me,
        you're an eejit (idiot) if you think a fecking flight is 50p!
    \endchorus
\endsong
