% vim: ft=tex

\stepcounter{subsection}

\beginsong{Scotland The Brave}[%
    by={John McDermott},
    cr={co},
    li={li},
    index={scotland_the_brave}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{Scotland The Brave} --- John McDermott}

    \label{scotland_the_brave}

    \beginverse\memorize[verse]
        Let Italy boast of her gay gilded waters
        Her vines and her bowers and her soft sunny skies
        Her sons drinking love from the eyes of her daughters
        Where freedom expires amid softness and sighs
    \endverse

    \beginchorus\memorize[chorus]
        Scotland's blue mountains wild where hoary clifs are piled,
        Towering in grandeur are dearer tae me.
        Land of the misty cloud land of the, tempest loud.
        Land of the brave and proud, land of the free
    \endchorus

    \beginverse\replay[verse]
        Enthroned on the peak of her own highland mountains,
        The spirit of Scotia reigns fearless and free.
        Her green tartan waving o'ver blue rock and fountain
        And proudly she sings looking over the sea.
    \endverse

    \beginchorus\replay[chorus]
        Here among my mountains wild, I  have serenely smiled
        When armies and empires against me were hurled.
        Firm as my native rock, I have withstood the shock
        Of England, of Denmark, of Rome and the world.
    \endchorus

    \beginverse\replay[verse]
        But see how proudly her ware steeds are prancing.
        Deep groves of steel trodden down in their path.
        The eyes of my sons like their bright swords are glancing,
        Triumphantly riding through ruin and death.
    \endverse

    \beginchorus\replay[chorus]
        Bold hearts and nodding plumes wave o'ver their bloody tombs
        Deep eyed in gore is the green tartan's wave.
        Shivering are the ranks of steel, dire is the horseman's wheel,
        Victorious in battlefield, Scotland the brave.
    \endchorus

    \beginverse\replay[verse]
        Hark, when the night is falling, hear, hear the pipes are calling
        Loudly and proudly calling down through the glen
        There where the hills are sleeping, now feel the blood a leaping
        High as the spirits of the hold highland men
    \endverse

    \beginchorus\replay[chorus]
        Towering in gallant fame, Scotland my mountain hame
        High may your proud stanards gloriously wave.
        Land o' the high endeavour, land o' the shining river
        Land o' my heart forever Scotland the brave.
    \endchorus
\endsong
