% vim: ft=tex:

\stepcounter{subsection}

\beginsong{The green fields of France}[%
    by={Eric Boyle},
    index={thegreenfieldsoffrance}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{The green fields of France} --- Eric Boyle}

    \label{thegreenfieldsoffrance}

    \begin{center}
        \gtab{G}{320033:210034}
        \gtab{Em}{022000:023000}
        \gtab{Am}{X02210:002310}
        \gtab{Am/C}{X32210:042310}
        \gtab{D7}{XX0212:000213}
        \gtab{C}{332010:342010}
    \end{center}

    \beginverse\memorize[verse]
        Well h\[G]ow do you d\[Em]o, young W\[Am]illie McBr\[Am/C]ide,
        Do you m\[D7]ind if I sit here down b\[G]y your gr\[C]aves\[G]ide
        And r\[G]est for a wh\[Em]ile in the w\[Am]arm summer s\[Am/C]un,
        I've been w\[D7]orking all day and I'm n\[G]ear-l\[D]y d\[G]one?
        \brk
        I can s\[G]ee by your gr\[Em]avestone you were \[Am]only ninet\[Am/C]een,
        When you j\[D7]oined the great fallen in n\[G]ineteen-s\[Dsus4]ixteen \[D]
        Well, I h\[G]ope you died w\[Em]ell and I h\[Am]ope you died cl\[Am/C]ean,
        Or young W\[D7]illie McBride was it sl\[G]ow and \[D]obsc\[G]ene.
    \endverse

    \beginchorus\memorize[chorus]
        Did they b\[D]eat the drum slowly and pl\[C]ay the fife l\[G]owly?
        Did they s\[D]ound the death march, as they l\[C]owered you d\[G]own?
        And did the b\[C]and play the last post and ch\[D]orus?
        And did the p\[G]ipes play the fl\[C]oweres of the F\[D]o\[Dsus2]-\[D]-r\[G]est.
    \endchorus

    \beginverse\replay[verse]
        Did you l^eave a wife ^ or a sw^eetheart beh^ind?
        In s^ome faithful heart is your m^emory ^enshr^ined,
        Alth^ough you died b^ack in n^ineteen-sixt^een,
        In th^at faithful heart you are for^ever n^inet^een.
        \brk
        Or ^are you a str^anger without ^even a n^ame,
        Encl^osed and forever beh^ind a gla^ss frame ^
        In an ^old photogr^aph torn and b^attered and st^ained
        And f^ading to yellow in a br^own leath^er fr^ame.
    \endverse

    \beginchorus\replay[chorus]
        Did they b^eat the drum slowly and pl^ay the fife l^owly?
        Did they s^ound the death march, as they l^owered you d^own?
        And did the b^and play the last post and ch^orus?
        And did the p^ipes play the fl^oweres of the F^o^-^-r^est.
    \endchorus

    \beginverse\replay[verse]
        The s^un now it shi^nes on the gr^een fields of Fr^ance.
        There's a w^arm summer breeze that makes the r^ed puppi^es d^ance.
        And l^ook how the s^un shines from ^under the tr^ee,
        There's no g^as, no barbed wire, no g^uns fir^ing n^ow.
        \brk
        But h^ere in this gr^aveyard it's st^ill ``No man's L^and'',
        The c^ountless white crosses lay m^ute und the ^ sand. ^
        To m^an's blind ind^ifference to h^is fellow m^an,
        To a wh^ole generation that were b^utchered ^and d^amned.
    \endverse

    \beginchorus\replay[chorus]
        Did they b^eat the drum slowly and pl^ay the fife l^owly?
        Did they s^ound the death march, as they l^owered you d^own?
        And did the b^and play the last post and ch^orus?
        And did the p^ipes play the fl^oweres of the F^o^-^-r^est.
    \endchorus

    \beginverse\replay[verse]
        Ah, young W^illie McBr^ide I can't h^elp wonder wh^y
        Do ^all those who lay here kn^ow why they d^id d^ie,
        and d^id they bel^ieve when they ^answered the c^all,
        Did they r^eally believe that this w^ar would ^end w^ars?
        \brk
        Well, the s^orrow, the s^uffering, the gl^ory and the p^ain,
        The k^illing and the dying were ^all done in ^ vain ^.
        For young W^illie McBr^ide it all h^appened ag^ain,
        and ag^ain, and again, and ag^ain, and ^ag^ain!
    \endverse

    \beginchorus\replay[chorus]
        \lrep Did they b^eat the drum slowly and pl^ay the fife l^owly?
        Did they s^ound the death march, as they l^owered you d^own?
        And did the b^and play the last post and ch^orus?
        And did the p^ipes play the fl^oweres of the F^o^-^-r^est. \rrep \rep{2}
    \endchorus
\endsong
