\stepcounter{subsection}

\beginsong{The Enchanter}[%
    by={Larp-Lieder.de},
    index={theenchanter}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{The Enchanter} --- \textit{Larp-Lieder.de}}

    \label{theenchanter}

    \begin{center}
        \gtab{G}{320033:210034}
        \gtab{C}{332010:342010}
        \gtab{D7}{XX0212:000312}
    \end{center}

    \beginverse\memorize[verse]
        I've b\[G]een an enchanter for many a y\[C]ear
        And I've s\[G]ent all my m\[C]oney on s\[D7]mall boys and b\[G]eer.
        But n\[G]ow I'm returning with spells in great st\[C]ore,
        And I n\[G]ever will pl\[C]ay the appr\[D7]entice, no m\[G]ore.
    \endverse

    \beginchorus\memorize[chorus]
        And it's n\[D]o, nay, never, \[G] no, nay, never no m\[C]ore
        Will I pl\[G]ay the appr\[C]entice, no n\[D7]ever, no m\[G]ore.
    \endchorus

    \beginverse\replay[verse]
        Well I w^ent to a guild house I used to frequ^ent,
        And I t^old the guildm^aster my w^and it was b^end,
        I ^asked him to fix it, he answered me y^es,
        And j^ust where he r^ammed it, I'll l^eave you to gu^ess.
    \endverse

    \beginchorus\replay[chorus]
        And it's n^o, nay, never, ^ no, nay, never no m^ore
        Will I pl^ay the appr^entice, no n^ever, no m^ore.
    \endchorus

    \beginverse\replay[verse]
        I w^ent down to norham a-selling my w^ares,
        But l^ooking ar^ound I n^oticed their st^ares.
        I w^ondered what's with them, but realy who c^ares?
        But I was s^o out of f^ashion I was st^ill wearing fl^ares.
    \endverse

    \beginchorus\replay[chorus]
        And it's n^o, nay, never, ^ no, nay, never no m^ore
        Will I pl^ay the appr^entice, no n^ever, no m^ore.
    \endchorus

    \beginverse\replay[verse]
        My st^ory is over, all told it is tr^ue,
        But ^one word for w^isdom I'll l^eave with y^ou.
        If y^ou get apprenticed to magic say ``n^ay'',
        But pl^ease don't off^end, or they'll bl^ow you aw^ay.
    \endverse

    \beginchorus\replay[chorus]
        \lrep And it's n^o, nay, never, ^ no, nay, never no m^ore
        Will I pl^ay the appr^entice, no n^ever, no m^ore. \rrep \rep{2}

        \textnote{1\textsuperscript{st} time kind of a.c.}
    \endchorus
\endsong
