% vim: ft=tex:

\stepcounter{subsection}

\beginsong{The bonny ship the diamond}[%
    by={\textit{Traditional}},
    index={thebonnyshipthediamond}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{The bonny ship the diamond} --- \textit{Traditional}}

    \label{thebonnyshipthediamond}

    \begin{center}
        \gtab{Am}{X02210:002310}
        \gtab{Em}{022000:023000}
        \gtab{Em7}{020000:020000}
    \end{center}

    \beginverse\memorize[verse]
        The D\[Am]iamond is a sh\[Em]ip me lads, for the D\[Am]avid Straits she's b\[Em]ound
        And the q\[Am]uay it is all g\[Em]arnished with b\[Am]onny l\[Em7]assies 'r\[Am]ound.
        Captain Th\[Am]ompson gives the \[Em]order to s\[Am]ail the ocean w\[Em]ide
        Where the s\[Am]un it never s\[Em]ets me lads, nor d\[Am]arkness d\[Em7]ims the sk\[Am]y
    \endverse

    \beginchorus\memorize[chorus]
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus

    \beginverse\replay[verse]
        Al^ong the quay at P^eterhead the l^assies stand ar^ound
        With their sh^awls pulled all ab^out them and the s^alt te^ars running d^own.
        D^on't you weep me b^onny lassie, though y^ou'll be left beh^ind
        For the r^ose that grows on Gr^eenland's ice bef^ore I ch^anged my m^ind.
    \endverse

    \beginchorus\replay[chorus]
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus

    \beginverse\replay[verse]
        Here's h^ealth to the Resol^ution, likew^ise the Eliza S^wan.
        Here's h^ealth to the Battler of M^ontrose and the D^iamond sh^ip of f^ame.
        We w^ear the trousers ^of the white and the j^ackets of the bl^ue
        When w^e return to P^eterhead we'll h^ae sweeth^earts en^ou'.
    \endverse

    \beginchorus\replay[chorus]
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus

    \beginverse\replay[verse]
        ^It'll be bright both d^ay and night when the Gr^eenland lads come h^ame
        With a sh^ip that's full of ^oil me lads and m^oney t^o our n^ame.
        We'll m^ake the cradles f^or to rock and the bl^ankets for to t^ear
        And ^ev'ry lass in P^eterhead sing H^ush a b^ye me d^ear
    \endverse

    \beginchorus
        \textnote{2x}
        So it's cheer up me lads, let your hearts never fail.
        For the bonny ship the Diamond goes a fishing for the whale
    \endchorus
\endsong
