\stepcounter{subsection}

\beginsong{I see Fire}[%
    by={Ed Sheeran},
    index={iseefire}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{I see Fire} --- Ed Sheeran}

    \label{iseefire}

    \capo{6}

    \gtab{Em}{022000:023000}
    \gtab{C9}{032033:021034}
    \gtab{Dsus4/F#}{2X0233:100234}
    \gtab{Am}{X02210:002310}
    \gtab{C}{032010:032010}
    \gtab{G}{320033:210034}

    \beginverse*
        \textnote{a.c.}
        Oh, misty eye of the mountain below
        Keep careful watch of my brother's souls.
        And should the sky be filled with fire and smoke,
        Keep watching over Durin's son.
    \endverse

    \beginverse
        If this is to \[Em]end in \[C9]fire
        then we should \[Dsus4/F#]all burn tog\[Em]ether.
        Watch the fl\[Em]ames climb \[C9]high \[Dsus4/F#]into the \[Em]night.
        Calling \[Em]out for \[C9]the rope, \[Dsus4/F#]sent by and \[C9]we will
        Watch the \[Am]flames burn \[C]on and on the \[Em]mountain \[C9]side
    \endverse

    \beginverse
        And if we should \[Em]die to\[C9]night
        Then we should \[Dsus4/F#]all die tog\[Em]ether.
        Raise a \[Em]glass of \[C9]wine \[Dsus4/F#] for the \[Em]last time.
        Calling \[Em]out for \[C9]the rope, \[Dsus4/F#]prepare as \[C9]we will.
        Watch the \[Am]flames burn \[C]on and on the \[Em]mountain \[C9]side.
        Desol\[Am]ation \[C]comes upon the \[C9]sky \[Dsus4/F#]
    \endverse

    \beginchorus
        Now I see \[Em]fire, \[C9] \[Dsus4/F#]inside the \[Em]mountain
        And I see \[Em]fire, \[C9] \[Dsus4/F#]burning the \[Em]trees.
        And I see \[Em]fire, \[C9] \[Dsus4/F#]hollowing \[Em]souls.
        And I see \[Em]fire, \[C9] \[Dsus4/F#]burning the \[Em]breeze.
        And I'll \[Em]hope that you'll remember me \textnote{let ring}
    \endchorus

    \brk

    \beginverse
        Or should my \[Em]people \[C9]fall then
        Surely \[Dsus4/F#]I'll do the \[Em]same
        Confined in \[Em]mountain \[C9]halls we
        Got to \[Dsus4/F#]close to the \[Em]flame
        Calling \[Em]out fath\[C9]er \[Dsus4/F#]hold fast and \[C9]we will
        Watch the \[Am]flames burm \[C]on and on the \[Em]mountain \[C9]side
        Desol\[Am]ation \[C]comes upon the \[C9]sky \[Dsus4/F#]
    \endverse

    \beginchorus
        Now I see \[em]fire, \[c9] \[d]inside the \[em]mountain
        And I see \[em]fire, \[c9] \[d]burning the \[em]trees.
        And I see \[em]fire, \[c9] \[d]hollowing \[em]souls.
        And I see \[em]fire, \[c9] \[d]burning the \[em]breeze.
        And I'll \[em]hope that you'll remember me \textnote{let ring}
    \endchorus

    \beginverse*
        And if the \[Am]night is \[Em]burning
        I will \[G]cover mhy \[Dsus4/F#]eyes
        For if the \[Am]dark ret\[Em]urns then
        My br\[G]others will \[Dsus4/F#]die
        And as the \[Am]sky is falling \[Em]down
        It crashed in\[G]to this lonely \[Dsus4/F#]town.
        And with the \[Am]shadow upon the ground
        I hear my \[C9]people screaming \[Dsus4/F#]out.
    \endverse

    \beginchorus
        \textnote{8va und \textit{ff}}
        Now I see \[Em]fire, \[C9] \[Dsus4/F#]inside the \[Em]mountain
        And I see \[Em]fire, \[C9] \[Dsus4/F#]burning the \[Em]trees.
        And I see \[Em]fire, \[C9] \[Dsus4/F#]hollowing \[Em]souls.
        And I see \[Em]fire, \[C9] \[Dsus4/F#]burning the \[Em]breeze.
    \endchorus

    \beginchorus
        Now I see \[Em]fire, \[C9] \[Dsus4/F#]inside the \[Em]mountain \echo{Oh you know I saw a city burning}
        And I see \[Em]fire, \[C9] \[Dsus4/F#]burning the \[Em]trees \echo{Feel the heat upon my skin}
        And I see \[Em]fire, \[C9] \[Dsus4/F#]hollowing \[Em]souls \echo{Who ooh ooh ...}
        And I see \[Em]fire, \[C9] \[Dsus4/F#]burning the \[Em]breeze \echo{Burning on and on the mountain side}
    \endchorus
\endsong
