\stepcounter{subsection}

\beginsong{I courted a wee girl}[%
    by={\textit{Traditional}},
    index={icourtedaweegirl}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{I courted a wee girl} --- \textit{Traditional}}

    \label{icourtedaweegirl}

    \textbf{Note: this song is not yet finished!}

    \beginverse
        I courted a wee girl for many's the long day,
        And slighted all others who came in my way.
        But now she's rewarded me to the last day,
        She's gone to be wed to another.
    \endverse

    \beginverse
        The bride and bride's party to church they did go.
        The bride she rode foremost she put the best show
        And I rode behind my heart filled with woe
        To see my love wed to another.
    \endverse

    \beginverse
        The bride and bride's party, in church they did stand,
        Gold rings on their fingers, a love hand in hand.
        The man that she's wed to has houses and land;
        He may have her since I could not gain her.
    \endverse

    \beginverse
        The last time I saw her she was all dressed in white,
        The more I gazed on her she dazzled my sight,
        So I tipped her my hat and bade her goodnight.
        Here's bad luck to all false-hearted lovers.
    \endverse

    \beginverse
        So dig me a grave and dig it down deep,
        And strew it all over with primerose so sweet.
        And lay me down in it for no more for to weep,
        For love was the cause of my ruin.
    \endverse
\endsong
\wpage
