\stepcounter{subsection}

\beginsong{Rolling in the deep}[%
    by={Adele},
    index={rollinginthedeep}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{Rolling in the deep} --- Adele}

    \label{rollinginthedeep}

    \begin{center}
        \gtab{Am}{002210:002310}
        \gtab{Em}{022000:023000}
        \gtab{G}{320033:210034}
        \gtab{F}{133211:134211}
    \end{center}

    \beginverse
        \[Am]There's a fire start\[Em]ing in my heart,
        \[G]Reaching a fever pitch, and it's bring\[Em]ing me out the dark. \[G]
        \[Am]Finally, I can see \[Em]you crystal clear,
        \[G]Go ahead and sell me out, and I'll \[Em]lay your ship bare. \[G]
    \endverse

    \beginverse
        ^See how I'll leave with ^every piece of you,
        ^Don't underestimate the things ^atht I will do. ^
        ^There's a fire start^ing in my heart,
        ^Reaching a fever pitch, and it's bring^ing me out the dark. ^
    \endverse

    \beginverse*
        \[F] The scars of \[G]your love remind me \[Em]of us,
        They keep me \[F]thinking that we almost had it \[F]all,
        The scars of \[G]your love, they leave me \[Em]breathless
        I can't help feeling ...
    \endverse

    \beginchorus
        We could have had it \[Am]a\[G]ll
        Rolling in the \[F]deep,
        You had \[G]my heart in\[Am]side,
        of your \[G]hand, and you \[F]played it to the beat. \[G]
    \endchorus

    \beginverse
        ^Baby, I have no stor^y to be told,
        But ^I've heard of one of you and I'm gonna ^make your head burn. ^
        ^Think of me in the depths ^of your despair,
        ^Make a home down there as mine ^sure won't be shared. ^
    \endverse

    \beginverse*
        \[F] The scars \[G]your love remind me \[Em]of us,
        They keep me \[F]thinking that we almost had it \[F]all.
        The scars of \[G]your love, they leave me br\[Em]eathless,
        I can't help feeling ...
    \endverse

    \beginchorus
        We could have had it \[Am]a\[G]ll
        Rolling in the \[F]deep,
        You had \[G]my heart in\[Am]side,
        of your \[G]hand, and you \[F]played it to the beat. \[G]
    \endchorus

    \beginchorus
        We \[G]could have had it \[F]a\[G]ll
        Rolling in the \[Am]deep, \[G]
        You had my heart in\[F]side,
        of your hand, and you \[F]played it to the \[G]beating. \[G]
    \endchorus

    \beginverse
        \textnote{a.c.}
        Throw your soul through every open door,
        Count your blessings to find what you look for.
        Turn my sorrow into treasured gold,
        You'll pay me back in kind and reap just what you sow \[Am] \[G]
    \endverse

    \beginverse*
        We could have had it \[F]all,
        We could have had it \[Am]all, \[G]
        it \[F]all ...
        it \[F]all ...
        it \[F]all ...
    \endverse

    \beginchorus
        We \[G]could have had it \[Am]a\[G]ll
        Rolling in the \[F]deep,
        You had \[G]my heart in\[Am]side,
        of your \[G]hand, and you \[F]played it to the beating
        \[G]could have had it \[Am]a\[G]ll.
        Rolling in the \[F]deep,
        You \[G]had my heart in\[Am]side,
        of your \[G]head.
        But you \[F]played it,
        You \[F]played it,
        You \[F]played it,
        You \[F]played it to the \[Am]beat.
    \endchorus
\endsong
