\stepcounter{subsection}

\beginsong{The Enchanter}[%
    by={Larp-Lieder.de},
    index={theenchanter}]

    \phantomsection
    \addcontentsline{toc}{subsection}{\thesubsection \quad \textbf{The Enchanter} --- \textit{Larp-Lieder.de}}

    \label{theenchanter}

    \begin{center}
        \gtab{G}{320033:210034}
        \gtab{C}{332010:342010}
        \gtab{D7}{XX0212:000312}
    \end{center}

    \beginverse
        I've \[G]been an enchanter for many a \[C]year
        And I've \[G]sent all my \[C]money on \[D7]small boys and \[G]beer.
        But \[G]now I'm returning with spells in great \[C]store,
        And I \[G]never will \[C]play the ap\[D7]prentice, no \[G]more.
    \endverse

    \beginchorus
        And it's \[D]no, nay, never, \[G] no, nay, never no \[C]more
        Will I \[G]play the ap\[C]prentice, no \[D7]never, no \[G]more.
    \endchorus

    \beginverse
        Well I ^went to a guild house I used to fre^quent,
        And I ^told the guild^master my ^wand it was ^bend,
        I ^asked him to fix it, he answered me ^yes,
        And ^just where he ^rammed it, I'll ^leave you to ^guess.
    \endverse

    \beginchorus
        And it's \[D]no, nay, never, \[G] no, nay, never no \[C]more
        Will I \[G]play the ap\[C]prentice, no \[D7]never, no \[G]more.
    \endchorus

    \beginverse
        I ^went down to norham a-selling my ^wares,
        But ^looking a^round I ^noticed their ^stares.
        I ^wondered whats with them, but realy who ^cares?
        But I was ^so out of ^fashion I was ^still wearing ^flares.
    \endverse

    \beginchorus
        And it's \[D]no, nay, never, \[G] no, nay, never no \[C]more
        Will I \[G]play the ap\[C]prentice, no \[D7]never, no \[G]more.
    \endchorus

    \beginverse
        My ^story is over, all told it is ^true,
        But ^one word for ^wisdom I'll ^leave with ^you.
        If ^you get apprenticed to magic say ^``nay'',
        But ^please don't off^end, or they'll ^blow you a^way.
    \endverse

    \beginchorus
        \lrep And it's \[D]no, nay, never, \[G] no, nay, never no \[C]more
        Will I \[G]play the ap\[C]prentice, no \[D7]never, no \[G]more. \rrep \rep{2}

        \textnote{1\textsuperscript{st} time a.c.}
    \endchorus
\endsong
